Gamification Effectiveness on Education

### 2024-04-18 paper/paper.qmd
added info about gender in results
added replication link

---
title: "Gamification Effectiveness on Education"
author: 
  - Sachin Chhikara
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

>>>>

---
title: "Gamification Effectiveness on Education"
author: 
  - Sachin Chhikara
thanks: "Code and data are available at: https://github.com/SachinChhikara/Effectiveness_of_Gamification_Education."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Males overall on average did better than females by 2-3%. Also, males in the gamification plugin group on average did better that females by 1-2%.  Interestingly, males do 2-4% worse than females in educational game, social gamification and social network group.
